Differentially Private Bayesian Inference

### 2018-04-10 main.tex
update

\subsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the dilation property holds:

@@

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(z)}{h(e^{\lambda}z)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\expomech) (1 - e^{\lambda})}{S(x)})$. Consider the event $G = \{ \expomech : u(\expomech) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(z)$ is $1 - \frac{\delta}{2}$. Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$. The $\beta$ is set as

@@

\end{itemize}
% So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.

>>>>

\subsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\expomech$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, the dilation property holds:

@@

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(z)}{h(e^{\lambda}z)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\expomech) (1 - e^{\lambda})}{S(x)})$. Consider the event $G = \{ \expomech : u(\expomech) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(z)$ is $1 - \frac{\delta}{2}$. Thus, the probability of a given event $z$ is at most $Pr[z \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}z] + \frac{\delta}{2}$.

% \sout{
\begin{itemize}

@@

\end{itemize}
% }
% So, we only need to proof it in two cases where $\lambda > 0, u(x,r) < 0$ and $\lambda < 0, u(x,r) > 0$.
